A Way Forward in Parallelising Dynamic Languages

### 2014-05-05 talk/icooolps2014/position-paper.tex
another citation

TM can be implemented in software (STM) or in hardware (HTM). There
are also hybrid approaches, which combine the two. We count these
hybrid approaches as STM, since they usually provide the same
capabilities as software-only approaches but with different
performance characteristics. We will now first look at HTM, which
recently gained a lot of popularity by its introduction in common
desktop CPUs from Intel (Haswell generation).\cfbolz{citation}

@@

>>>>

TM can be implemented in software (STM) or in hardware (HTM). There
are also hybrid approaches, which combine the two. We count these
hybrid approaches as STM, since they usually provide the same
capabilities as software-only approaches but with different
performance characteristics. We will now first look at HTM, which
recently gained a lot of popularity by its introduction in common
desktop CPUs from Intel (Haswell generation)~\cite{odaira14,leis14}.

@@

\bibitem{leis14}
  Leis, Viktor, Alfons Kemper, and Thomas Neumann. "Exploiting
  Hardware Transactional Memory in Main-Memory Databases."
  \emph{Proc. of ICDE}. 2014.
